A Type System for Safe and Scalable Parallelism using Logical Regions

### 2012-07-04 doc/popl2013/related.tex
Adding some more related work

Separation Logic is another mechanism that can be used for reasoning about disjointness
of program data \cite{Reynolds02}. %Still not sure what we want to put here.
% DPJ sites additional separation logic papers but they didn't seem very similar.
% Let me know if you think we should include them as well.

Chapel\cite{Chamberlain:Chapel} and X10 \cite{X1005} are similar parallel programming
models to Legion.  Chapel's domains and X10's places provide the programmer with a 
mechanism for expressing locality similar to regions in Legion.  However, domains
and places are not used in any way for independence analysis for discovering parallelism.
Jade is a parallel programming mode that relies on programmer annotations to describe
data disjointness\cite{Rinard98}.  Jade then leverages this disjointness information
to implicitly discover parallelism similar to Legion.

>>>>

Separation Logic is another mechanism that can be used for reasoning about disjointness
of program data \cite{Reynolds02}.  Concurrent separation logic\cite{Brookes04} has been 
used both to parallelize sequential programs\cite{Raza09,Gotsman07} and to provide 
a mechanism for reasoning about independence\cite{Hayman06}.
While we adopted some notation from separation logic, we ultimately chose to use a 
type and effect system as our primary formalism because separation logic cannot easily 
describe the interleaving of effects to non-disjoint regions of memory.
%Still not sure what we want to put here.
% DPJ sites additional separation logic papers but they didn't seem very similar.
% Let me know if you think we should include them as well.

Chapel \cite{Chamberlain:Chapel} and X10 \cite{X1005} are similar parallel programming
models to Legion.  Chapel's domains and X10's places provide the programmer with a 
mechanism for expressing locality similar to regions in Legion.  However, domains
and places are not used in any way for independence analysis for discovering parallelism.
Jade is a parallel programming mode that relies on programmer annotations to describe
data disjointness\cite{Rinard98}.  Jade then leverages this disjointness information
to implicitly discover parallelism similar to Legion.
